---
title: "FoodC5 Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FoodC5}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo = TRUE, include = FALSE}
library(C50)
library(pander)
library(FoodC5)
```


## Retrieve fuzzy scores and predict mapping using a pre-trained model


Retrieve pre-computed fuzzy scores for English food names and use a pre-trained C5.0 model to
classify results as good or bad matches.
Fuzzy matching scores can be computed using the Foodmapping R package.

```{r , echo = TRUE}
data(food_score)
preds <- c5_one_language(food_score,  'ENG_SCORE', 'EDIFF')
pander(head(preds), split.table = Inf )
```

The same approach can also be made, using a comparison of the original food
name. 

```{r , echo = TRUE}
preds <- c5_one_language(food_score,  'ORI_SCORE', 'EDIFF', c5_object = read_c50_ori() ) 
pander(head(preds), split.table = Inf )
```


## Explore the C5.0 tree 

Summary of the defaut English Based C5.O tree

```{r , echo = TRUE}
eng_tree <- read_c50_eng()
summary(eng_tree)
```




